%-------------------------
% Resume in Latex
% Author : Alex Korde
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
%\usepackage{TimesNewRoman}
 \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Alex Korde} \\ \vspace{1pt}
    \small 804-312-7873 $|$ \href{mailto:x@x.com}{\underline{alexkorde@icloud.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{https://www.linkedin.com/in/alexkorde?utm_source=share_via&utm_content=profile&utm_medium=member_ios}} $|$
    \href{https://github.com/...}{\underline{github.com/AlexKorde}}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Virginia}{Charlottesville, VA}
      {Bachelor of Arts in Mathematics, Concentration in Financial Mathematics}{August 2024 -- May 2027}
      \resumeSubheading
      {Virginia Commonwealth University}{Richmond, VA}
      {Economics}{August 2022 -- April 2024}
    
  \resumeSubHeadingListEnd
   
\section{Projects}
    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{CFP aNILyzer: Predictive Market Modeling} $|$ \emph{Python, Scikit-Learn, Pandas}}{January 2026 -- June 2026}
          \resumeItemListStart
            \resumeItem{Designed era-normalisation framework to control for structural shifts in offensive production across seasons, enabling valid cross-era team comparisons}
            \resumeItem{Engineered interaction terms (NIL era × stat differentials) to directly capture coefficient shifts across the regulatory break point (2021)}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Optimization of Hydro-Turbine Efficiency} $|$ \emph{Python, Multivariate Calculus, MATLAB}}{July 2024 -- August 2024}
          \resumeItemListStart
            \resumeItem{Formulated a constrained optimization model to maximize hydro-turbine power output relative to blade surface area and fluid velocity.}
            \resumeItem{Simulated efficiency gradients in MATLAB, providing a quantitative basis for identifying peak operational performance.}
            \resumeItem{Calculated the stationary points of the Lagrangian function $\mathcal{L}(x, y, \lambda) = f(x, y) - \lambda(g(x, y) - c)$ to identify optimal blade geometry.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Advanced Statistical Practicum} $|$ \emph{IBM SPSS, Methodological Modeling}}{January 2024 -- May 2024}
          \resumeItemListStart
            \resumeItem{Executed Multiple Linear Regression and ANOVA on complex datasets to identify significant variables and correlations, utilizing IBM SPSS for all data wrangling and analysis.}
            \resumeItem{Conducted Inference on Categorical Data using Chi-square tests for independence to interpret contingency tables and distribution-free (nonparametric) methods.}
            \resumeItem{Designed and analyzed Randomized Block Designs, applying rigorous hypothesis testing to validate experimental results.}
          \resumeItemListEnd
    
          \resumeProjectHeading
          {\textbf{Business Simulation} $|$ \emph{Excel, Team Cohesion}}{January 2023 -- May 2023}
          \resumeItemListStart
            \resumeItem{Developed a comprehensive financial model currently utilized by the department as the benchmark "Gold Standard" for future curriculum instruction.}
            \resumeItem{Orchestrated a strategic team restructuring, pivoting from a 6-member to a 4-member high-performance unit to restore project velocity and accountability.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Athletic Tutor}{June 2023 -- April 2026}
      {Virginia Commonwealth University, Student-Athlete Support Services}{Richmond, VA}
      \resumeItemListStart
        \resumeItem{Managed a longitudinal caseload of students, analyzing performance patterns to optimize individualized instructional strategies.}
        \resumeItem{Facilitated fluency in business statistics and data interpretation through the systematic breakdown of complex analytical models.}
      \resumeItemListEnd
      

    \resumeSubheading
      {Content Tutor}{September 2024 -- June 2025}
      {University of Virginia, Cavalier Academic Support Team}{Charlottesville, VA}
      \resumeItemListStart
        \resumeItem{Translated abstract multivariate calculus and probability concepts into applied frameworks for student-athletes.}
        \resumeItem{Formulated structured problem-solving methodologies to bridge gaps in quantitative reasoning and statistical interpretation.}
        
    \resumeItemListEnd


  \resumeSubHeadingListEnd




%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{description}
    \item[Programming:] Python (Scikit-Learn, Pandas), MATLAB, Julia, SPSS, \textbf{\LaTeX}, C, Lua, Java
    \item[Mathematics:] Statistical Modeling, Probability Theory, Calculus, Differential Equations, Logistic Regression, ANOVA, Interaction Modeling
\end{description}


%-------------------------------------------
\end{document}
